### 2015-09-24 inst/vign/taxize_vignette.Rmd
updated vignettes

```{r resolvenames}
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
head( temp$results )
```

@@

* `get_boldid()`
* `get_colid()`
* `get_eolid()`
* `get_gbifid()`
* `get_nbnid()`
* `get_tpsid()`
* `get_ubioid()`

>>>>

```{r resolvenames}
temp <- gnr_resolve(names = c("Helianthos annus", "Homo saapiens"))
head(temp)
```

@@

* `get_boldid()`
* `get_colid()`
* `get_eolid()`
* `get_gbifid()`
* `get_nbnid()`
* `get_tpsid()`
